Deciding Bitvector Termination with Program Synthesis

### 2014-07-03 papers/termination/paper.tex
revised more of the kalashnikov section

\item Our proposed termination proving procedure can also prove non-termination. Alternating termination and non-termination?

@@

\section{Solving the Synthesis Formula} \label{sec:synthesis}
%
\iffalse
\subsection{The Search Space and the Kolmogorov Complexity of a Ranking Function}
\begin{conjecture}
The lexicographic ordering does not influence the size of the search space. Thus, finding potentially lexicographic termination arguments is not more difficult than finding non-lexicographic ones.   
\end{conjecture}

>>>>

\item Our proposed termination proving procedure can also prove non-termination: (non-)termination analysis.

@@

\section{Satisfiability of a Formula in the Synthesis Fragment} \label{sec:synthesis}
%
\iffalse
\subsection{The Search Space and the Kolmogorov Complexity of a Ranking Function}
\begin{conjecture}
The lexicographic ordering does not influence the size of the search space. Thus, finding potentially lexicographic termination arguments is not more difficult than finding non-lexicographic ones.   
\end{conjecture}
